Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-06-07 paper.tex
Fix line endings
Tidy affiliations and edit author order.

\author{
  Samuel E Adams$^8$%
  \email{Samuel E Adams - sea36@cam.ac.uk}
  \and
  Jonathan Alvarsson$^1$%
  \email{Jonathan Alvarsson - jonathan.alvarsson@farmbio.uu.se}
  \and
  Igor V Filippov$^2$%
  \email{Igor V Filippov - igorf@helix.nih.gov}
  \and
  Rajarshi Guha$^2$%
  \email{Rajarshi Guha - guhar@mail.nih.gov}
  \and
  Robert Hanson$^3$%
  \email{Robert Hanson - hansonr@stolaf.edu}
  \and
  Marcus D Hanwell$^{4}$%
  \email{Marcus D Hanwell - marcus.hanwell@kitware.com}
  \and
  Geoffrey R Hutchison$^5$%
  \email{Geoffrey R Hutchison - geoffh@pitt.edu}
  \and
  Karol M Langner$^6$%
  \email{Karol M Langner - langnerkm@chem.leidenuniv.nl}
  \and
  Daniel M Lowe$^8$%
 \email{Daniel Lowe - dl387@cam.ac.uk}
  \and
  Peter Murray-Rust$^8$%
  \email{Peter Murray-Rust - pm286@cam.ac.uk}
  \and
  Noel M O'Boyle\correspondingauthor$^9$%
  \email{Noel M O'Boyle\correspondingauthor - n.oboyle@ucc.ie}
  \and
  Dmitry Pavlov$^{10}$%
  \email{Dmitry Pavlov - dpavlov@ggasoftware.com}
  \and
  Ola Spjuth$^1$%
  \email{ola.spjuth@farmbio.uu.se}
  \and
  Christoph Steinbeck$^{11}$%
  \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
  \and
  Adam L Tenderholt$^{12}$%
  \email{Adam L Tenderholt - adamlt82@u.washington.edu}
  \and
  Kevin J Theisen$^{13}$%
  \email{Kevin J Theisen - kevin@ichemlabs.com}
  \and
  Egon L Willighagen$^{14}$%
  \email{Egon L Willighagen - egon.willighagen@ki.se}
}

@@

\address{%
    \iid(1)Department of Pharmaceutical Biosciences, Uppsala University, Box 591, 751 24 Uppsala, Sweden \\
    \iid(2)NIH Center for Translational Therapeutics, 9800 Medical  Center Drive, Rockville, MD 20878 \\
    \iid(3)... \\
    \iid(4)Kitware, Inc., 28 Corporate Drive, Clifton Park, NY 12065, USA \\
    \iid(5)Department of Chemistry, University of Pittsburgh, 219 Parkman Avenue, Pittsburgh, PA 15260, USA \\
    \iid(6)Gorlaeus Laboratories, Leiden University, 2333 CC Leiden, The Netherlands \\
    \iid(8)Unilever Centre for Molecular Sciences Informatics, Department of Chemistry, University of Cambridge, Lensfield Road, CB2 1EW, UK \\
    \iid(9)Analytical and Biological Chemistry Research Facility, Cavanagh Pharmacy Building, University College Cork, College Road, Cork, Co. Cork, Ireland \\
    \iid(10)GGA Software Services LLC, 41 Nab. Chernoi rechki 194342, Saint Petersburg, Russia \\
    \iid(11)Cheminformatics and Metabolism Team, European Bioinformatics Institute (EBI), Wellcome Trust Genome Campus, Hinxton, Cambridge, UK \\
    \iid(12)Department of Chemistry, University of Washington, Seattle, WA 98195 \\
    \iid(13)iChemLabs, 200 Centennial Ave., Suite 200, Piscataway, NJ 08854, USA \\
    \iid(14)Division of Molecular Toxicology, Institute of Environmental Medicine, %
        Nobels vaeg 13, Karolinska Institutet, 171 77 Stockholm, Sweden
}%

>>>>

\author{
  Noel M O'Boyle\correspondingauthor$^1$%
  \email{Noel M O'Boyle\correspondingauthor - baoilleach@gmail.com}
  \and
  Samuel E Adams$^2$%
  \email{Samuel E Adams - sea36@cam.ac.uk}
  \and
  Jonathan Alvarsson$^3$%
  \email{Jonathan Alvarsson - jonathan.alvarsson@farmbio.uu.se}
  \and
  Igor V Filippov$^4$%
  \email{Igor V Filippov - igorf@helix.nih.gov}
  \and
  Rajarshi Guha$^4$%
  \email{Rajarshi Guha - guhar@mail.nih.gov}
  \and
  Robert Hanson$^5$%
  \email{Robert Hanson - hansonr@stolaf.edu}
  \and
  Marcus D Hanwell$^{6}$%
  \email{Marcus D Hanwell - marcus.hanwell@kitware.com}
  \and
  Geoffrey R Hutchison$^7$%
  \email{Geoffrey R Hutchison - geoffh@pitt.edu}
  \and
  Karol M Langner$^8$%
  \email{Karol M Langner - langnerkm@chem.leidenuniv.nl}
  \and
  Daniel M Lowe$^2$%
  \email{Daniel Lowe - dl387@cam.ac.uk}
  \and
  Dmitry Pavlov$^{9}$%
  \email{Dmitry Pavlov - dpavlov@ggasoftware.com}
  \and
  Ola Spjuth$^3$%
  \email{ola.spjuth@farmbio.uu.se}
  \and
  Christoph Steinbeck$^{10}$%
  \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
  \and
  Adam L Tenderholt$^{11}$%
  \email{Adam L Tenderholt - adamlt82@u.washington.edu}
  \and
  Kevin J Theisen$^{12}$%
  \email{Kevin J Theisen - kevin@ichemlabs.com}
  \and
  Egon L Willighagen$^{13}$%
  \email{Egon L Willighagen - egon.willighagen@ki.se}
  \and
  Peter Murray-Rust$^2$%
  \email{Peter Murray-Rust - pm286@cam.ac.uk}
}

@@

\address{%
    \iid(1)Analytical and Biological Chemistry Research Facility, Cavanagh Pharmacy Building, University College Cork, College Road, Cork, Co. Cork, Ireland \\
    \iid(2)Unilever Centre for Molecular Sciences Informatics, Department of Chemistry, University of Cambridge, Lensfield Road, CB2 1EW, UK \\
    \iid(3)Department of Pharmaceutical Biosciences, Uppsala University, Box 591, 751 24 Uppsala, Sweden \\
    \iid(4)NIH Center for Translational Therapeutics, 9800 Medical  Center Drive, Rockville, MD 20878, USA \\
    \iid(5)St. Olaf College, 1520 St. Olaf Ave., Northfield, MN 55057, USA \\
    \iid(6)Kitware, Inc., 28 Corporate Drive, Clifton Park, NY 12065, USA \\
    \iid(7)Department of Chemistry, University of Pittsburgh, 219 Parkman Avenue, Pittsburgh, PA 15260, USA \\
    \iid(8)Gorlaeus Laboratories, Leiden University, 2333 CC Leiden, The Netherlands \\
    \iid(9)GGA Software Services LLC, 41 Nab. Chernoi rechki 194342, Saint Petersburg, Russia \\
    \iid(10)Cheminformatics and Metabolism Team, European Bioinformatics Institute (EBI), Wellcome Trust Genome Campus, Hinxton, Cambridge, UK \\
    \iid(11)Department of Chemistry, University of Washington, Seattle, WA 98195, USA \\
    \iid(12)iChemLabs, 200 Centennial Ave., Suite 200, Piscataway, NJ 08854, USA \\
    \iid(13)Division of Molecular Toxicology, Institute of Environmental Medicine, %
        Nobels vaeg 13, Karolinska Institutet, 171 77 Stockholm, Sweden
}%
